Universal Anonymous Signatures

### 2022-09-16 prism-backend/research/gsac/formal-uas.tex
In depth pass up to sec 3.1.

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage these keys to request credentials. This may
seem too ideal as a model for real world situations, as we cannot know how
many keys a user has generated. However, we argue that this can in fact be very
close to reality, where a well-known issuer, after properly identifying a user,
attests the (possibly blinded) public key this user proves control of. Indeed,
our model and syntax support exactly this approach, by allowing users to
leverage previously obtained credentials in order to request new ones.
A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
then uses each of these keys to request multiple credentials, then from the
point of view of our modelling, we see this \emph{cryptographically} as two
different users -- and, anyway, that same ``user'' cannot combine credentials
bound to different keys.

\paragraph{Users and issuers.} %
Finally, a relevant aspect of our approach is that users and issuers are
essentially the same thing: just an entity with a key pair. The difference is
that, when users wish to become issuers, they have to advertise their public
keys, along with their conditions for granting credentials. For simplicity, we
just assume that they somehow ``publish their public keys''. In practice, this
may be done in several ways, depending on the situation: self-signing, relying
on external PKIs, bulletin boards, etc.
%
This approach has actually been used before to model delegatable anonymous
credentials \cite{bcc+09}, and it turns out to be also very useful for our
approach to build ring signatures from \UAS.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans$ being the transcript
  of the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

        \procedure{$\OBTISS(\cid=(\cidi,\cidu),\uid,\iid,\attrs,$\\
          \hspace*{4.25em}$\lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, R \rangle \gets
          \langle \Obtain(\UK[\uid],\cidu,\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
          \hspace*{50pt} \Issue(\PRVIK[\iid],\cidi,\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets R \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})):
          \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\oid,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcfor d\in\bin: \cuid_d \gets \OWNR[\cscid_d] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
          \feval) \\
          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},
          \msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, the opener identifier \oid, and the identifiers of all
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values. For notational
  convenience, we overload this function and use \oid and \iid instead of the
  actual keys.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

>>>>

\paragraph{Users and credentials.} %
In our model, every single user may have multiple credentials. In this
setting, a perhaps too strict assumption we make is that, once a user gets
compromised, all of the credentials owned by that user are compromised too.
While there may be real world situations for which this is too aggressive, it is
certainly a worst-case scenario, and greatly simplifies the modelling.
%
% Somehow related, we model a scheme in which users generate their secret keys in
% a standalone way, and then leverage these keys to request credentials. This may
% seem too ideal as a model for real world situations, as we cannot know how
% many keys a user has generated. However, we argue that this can in fact be very
% close to reality, where a well-known issuer, after properly identifying a user,
% attests the (possibly blinded) public key this user proves control of. Indeed,
% our model and syntax support exactly this approach, by allowing users to
% leverage previously obtained credentials in order to request new ones.
% A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
% then uses each of these keys to request multiple credentials, then from the
% point of view of our modelling, we see this \emph{cryptographically} as two
% different users -- and, anyway, that same ``user'' cannot combine credentials
% bound to different keys.

\paragraph{Users and issuers.} %
A relevant aspect of our model is that users and issuers are basically the
same: an entity with a key pair. The difference is that, when users wish to
become issuers, they advertise their public keys, along with their conditions
for granting credentials. To simplify, we just assume that they somehow
``publish their public keys'', which can be done in several ways in practice.

\paragraph{Functional placeholders.} %
We use generic functions to capture, at the design level, that users need
to prove concrete claims over their private information. Looking a bit ahead,
the output of these functions is defined in terms of (subsets of) the users'
key, credentials and attributes, and signed message. But, during our modelling,
we are only concerned with preventing that the output of these functions can
be dishonestly altered, and with ensuring that it does not threaten privacy
beyond what is necessary or unavoidable to reach the flexibility we want.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans$ being the transcript
  of the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving user secret key \usk, opener public key \opk, 
  credentials \sCred, message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Run by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

      \begin{minipage}[t]{0.58\textwidth}

        \procedure{$\OBTISS(\stackrel{\cid}{\pcbox{(\cidi,\cidu)}},\uid,\iid,\attrs,
          \lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, R \rangle \gets
          \langle \Obtain(\UK[\uid],\cidu,\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
          \hspace*{50pt} \Issue(\PRVIK[\iid],\cidi,\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets R \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,
          \stackrel{\cscid_{0,1}}{\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})
            \rbrace_{i\in[n]}}})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
          \pcind \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\oid,\stackrel{\cscid_{0,1}}{\pcbox{
            \lbrace (\ccid_{0,i},\ccid_{1,i})
            \rbrace_{i\in[n]}}},\msg,\feval)$}{%
          \pcfor d\in\bin: \cuid_d \gets \OWNR[\cscid_d] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
          \feval) \\
          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},
          \msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, the opener public key \opk, and the public keys $\ipk_i$
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values. For notational
  convenience, we overload this function and use \oid and \iid instead of the
  actual keys.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.
    % $\boxed{x}$ means the issuer learns $x$, \dboxed{$y$} means the verifier
    % learns $y$, and \dotboxed{z} means the opener reveals $z$.
  }
  \label{fig:nizkrels}
\end{figure}
